A thesis draft

### 2018-11-28 res/sections/15-ArchitecturalImplementation.tex
Fix sentences

In this chapter we will dig into the actual architectural implementation, seeing
all the problems related to it and how they were solved. We will show all the
various attempts made, and we will discussion about the technological issue and
changes we had to perform.

@@

We tried Tacker to see if its functionalities were good enough to be
adopted in our testbed instead of Openbaton. Its complete integration with
Openstack, indeed, was the main reason for its testing. We felt like the product
was not fully ready to be used in a real deployment though, since it lacked of
options like SFC management and the fact that it only officially supported
Openstack and not other cloud platforms was another reason to prefer Openbaton
eventually.

@@

\subparagraph*{Deployment via Vagrant}
The deployment via Vagrant confirmed our expectations because it revealed to be
was always smooth. The downside of this approach was the lack of customization
and of component management. The possibility to remove or add Openbaton Modules
dynamically later become fundamental to us. On top of that, the Vagrant
deployment uses a hypervisor virtualization system (based on Virtual Box), in
contrast with our goal to build a fully container-based system.

\subparagraph*{Deployment via Docker Compose}
The deployment with Docker Compose turned out to be best of the three
possibilities. The Docker Compose configuration offered an unprecedented
configuration flexibility, with the possibility to deploy only selected modules.
On top of that, this method let us manage the Openbaton version freely, having
more control on update especially during the development of our components.
Additionally, using this Docker Compose configuration allowed us to seamlessly
integrate the monitoring tools Zabbix, in order to have the possibility to
graphically see the data fetch from Openbaton about the system state. Finally, a
Docker based solution seemed to be the best approach since all of our components
were meant to be put inside a Docker container.

@@

The impossibility to develop a custom VIM driver and VNFM manager lead us to
search for an alternative solution. Then, we started to work directly on the
VIM. The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful APIs. We called this simple backend \emph{Harbor}.

@@

\subsubsection{Ingress and Egress: Ironhide}
As just said, the whole framework needs to have and entry and an exit point.
These, defined as \emph{Ingress} and \emph{Egress} points, are performed by
\emph{Ironhide}. Ironhide acts like a hides the whole packet processing to the
sender $S$ and the receiver $R$. When a client $S$ performs a request to $R$,
the packet actually goes through Ironhide, who has an internal classifier that
it is able to recognize the type of connection and to choose the right NS the
packet has to go through. This process is fundamental since it keeps the
connection between $S$ and $R$ up, for both TCP and UDP based communications.
Since the connection need to be end-to-end, the state of the connections are
saved in the \emph{Roulette Controller} component.

>>>>

In this chapter we will dig into the actual architectural proposal, seeing
all the problems related to it and how they were solved. We will show all the
various attempts made, and we will discussion about the technological issue and
changes we had to perform.

@@

We tried Tacker to see if its functionalities were good enough to be adopted in
our testbed instead of Openbaton. Its complete integration with Openstack,
indeed, was the main reason for its testing. At the end though, we felt like the
product was not ready for a real production environment. SFC management and the
lack of support for alternative platforms other than Openstack was another
reason to prefer Openbaton eventually.

@@

\subparagraph*{Deployment via Vagrant}
The deployment via Vagrant confirmed our expectations because it revealed to be
always a smooth operation. The downside of this approach was the lack of
customization and component management. The possibility to remove or add
Openbaton Modules dynamically become later fundamental to us. On top of that,
the Vagrant deployment uses a hypervisor virtualization system (based on Virtual
Box), in contrast with our goal to build a fully container-based system.

\subparagraph*{Deployment via Docker Compose}
The deployment with Docker Compose turned out to be the best of the three
possibilities. The Docker Compose configuration offered an unprecedented
configuration flexibility, with the possibility to deploy only selected modules.
On top of that, this method let us to manage the Openbaton version freely,
having more control on update especially during the development of our
components. Additionally, using this Docker Compose configuration allowed us to
seamlessly integrate the monitoring tools Zabbix, in order to have the
possibility to graphically see the data fetch from Openbaton about the system
state. Finally, a Docker based solution seemed to be the best approach since all
of our components were meant to be put inside a Docker container.

@@

The impossibility to develop a custom VIM driver and VNFM manager led us to
search for an alternative solution. Then, we started to work directly on the
VIM. The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful APIs. We called this simple backend \emph{Harbor}.

@@

\subsubsection{Ingress and Egress: Ironhide}
As just said, the whole framework needs to have and entry and an exit point.
These, defined as \emph{Ingress} and \emph{Egress} points, are performed by
\emph{Ironhide}. Ironhide hides the whole packet processing to the sender $S$
and the receiver $R$. When a client $S$ performs a request to $R$, the packet
actually goes through Ironhide, who has an internal classifier that it is able
to recognize the type of connection and to choose the right NS the packet has to
go through. This process is fundamental since it keeps the connection between
$S$ and $R$ up, for both TCP and UDP based communications. Since the connection
need to be end-to-end, the state of the connections are saved in the
\emph{Roulette Controller} component.
